A highly-available move operation for replicated trees

### 2019-11-04 paper/move-op.tex
Update acknowledgements
Mention some stats about Isabelle proof in the evaluation section

@@

As mentioned in Section~\ref{sec:intro}, the work presented in this paper is especially interesting due to ubiquity of a tree-structured data model.
In future work we hope to build novel peer-to-peer distributed systems, such as a distributed file-system, that make essential use of our algorithm.

\begin{acks}
The authors wish to acknowledge the support of The Boeing Company and the EPSRC ``REMS: Rigorous Engineering for Mainstream Systems'' programme grant (EP/K008528).
% AWS credits from the AWS Educate program
\end{acks}

>>>>

\subsection{Evaluation of formal proof}

The formalisation of our algorithm, and the proofs of its properties as described in \S\ref{sec:proof}, have been formally checked by Isabelle/HOL.
Our proofs contain no unproven assumptions (i.e. no occurrences of the \textbf{sorry} keyword).
Checking all of the proofs takes 3.5 minutes on a 2018 MacBook Pro.

Besides the 60 lines of definitions given in Figure~\ref{fig:code}, our Isabelle/HOL formalisation consists of a further 2,166 lines of code.
Of this, we use 203 lines to prove that every node has a unique parent, 443 lines to prove that the tree contains no cycles, 450 lines to prove that move operations commute and replicas converge, 327 lines to prove the strong eventual consistency of our algorithm using the framework of Gomes et al.~\cite{Gomes:2017gy}, and 743 lines to define the executable variant of our algorithm (\S\ref{subsect.extracting}) and prove its equivalence to the abstract definitions of Figure~\ref{fig:code}.

@@

As mentioned in the introduction, our work is especially interesting due to the ubiquity of tree data models across many different computing systems.
In future work we hope to build novel peer-to-peer distributed systems, such as a distributed filesystem, based on our algorithm.

\begin{acks}
The authors wish to acknowledge the support of The Boeing Company and the EPSRC ``REMS: Rigorous Engineering for Mainstream Systems'' programme grant (EP/K008528).
Martin Kleppmann is supported by a Leverhulme Trust Early Career Fellowship and by the Isaac Newton Trust.
Our evaluation was conducted using AWS credits from the AWS Educate program.
Thank you to Marc Shapiro for feedback on a draft of this paper.
\end{acks}
